---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

ptwikiwords
===============================
> Words used in Portuguese Wikipedia

[![Travis-CI Build Status](https://travis-ci.org/dfalbel/ptwikiwords.svg?branch=master)](https://travis-ci.org/dfalbel/ptwikiwords)

This data-package contains a dataset with words used in a random sample from ~15.000
pages from the [Portuguese Wikipedia](https://pt.wikipedia.org/).

# Installing

It can be installed using:

```{r, eval = F}
devtools::install_github("dfalbel/ptwikiwords")
```

# Using

After installing the package, you can load the dataset using:

```{r}
library(ptwikiwords)
data(ptwikiwords)
head(ptwikiwords)
```

The dataset contains 3 columns:

* word: word, as is, found in Wikipedia pages
* count: number of times the word was found in the sample of Wikipedia pages
* check: wheter the word exists in the portuguese language

Here is a wordcloud of those words:

```{r, wordcloud}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(wordcloud))
words_filter <- ptwikiwords %>%
  filter(check == T) %>%
  slice(1:300)
wordcloud(words_filter$word, words_filter$count)
```


